Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-17 paper.tex
psom pipeline implementation

    \section{PSOM} 
        \subsection{summary} 
        \subsection{limitations of PSOM}
    \section{SPM} 
        \subsection{summary} 
        \subsection{limitations of SPM} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

    \section{PSOM} 
        \subsection{summary} 
        While Python is a popular programming language amongst
neuroinformaticians, it is not the only one that is commonly used. To address
the needs of the Matlab/Octave community, PSOM (Pipeline System for Octave and
Matlab) was developed. Similarly to Nipype, PSOM is easy-to-use, can run in
distributed environments and can interface with tools written in other
languages.

        \note{pipeline description}
        A pipeline in PSOM, is a series of connected jobs, which can be
represented as a directed acyclic graph. The pipeline itself is implemented 
using the Matlab/Octave data type. Each job within the pipeline
is assigned a unique name. There is only one mandatory field in the job
description (command). The remaining four optional fields include the list input
files (files_in), the list output files (files_out), the list of files to be
deleted after execution (files_clean) and any Octave or Matlab datatype
containing any remaining optional parameters necessary for job execution (opt).
Jobs in PSOM run in a protected environment where they only have access to the
parameters that are passed.

        In order to determine whether the opt field was correctly set, the
generic function \textit{psom_struct_defaults} may be applied. This function
will set the default values, ensure all mandatory fields were supplied and issue
warnings for all unidentified attributes.

        To define modules in PSOM, a special Octave/Matlab function type, known as "bricks"
is used. Bricks employ the same parameters as jobs but lack the file_clean
parameter. All bricks contain an opt.flag_test boolean flag, which, if set to
true, allows the user to perform a dry-run of the brick. A dry-run of a brick
consists of updating the default parameters and validating that the brick can
successfully execute with the parameters provided. Bricks also have an option to
specify the output folder (opt.output_folder) for brick outputs to be stored.

        The pipeline generator is an easy way to create complete pipelines with
minimal information provided. A pipeline generator may accept at most the
file_in and opt arguments. It then builds the pipeline based on this
information and the default parameters specified in each brick applied by the
pipeline generator.

        \note{pipeline execution}

        \note{debugging and provenance}

        \subsection{limitations of PSOM}
    \section{SPM} 
        \subsection{summary} 
        \subsection{limitations of SPM} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

       \section{other domains}
       	\subsection{pegasus}
